---
title: "Coursea Practical Machine Learning"
author: "Kazu Yama"
date: "4/26/2015"
output: html_document
---

First we load and cleanse the data,
Based on the distribution of pml_testing.csv, it makes sense
to trim the columns with mostly NA Div/0 like so

Remember to set seed to make reproduable result


```{r}
set.seed(88088)
dftrain<-read.table("/home/ubuntu/Downloads/pml-training.csv", header=T, sep=",", na.strings=c("#DIV/0!","","NA"))
df <- dftrain[,colSums(is.na(dftrain))<nrow(dftrain)-1000]
print ("dimension of orignal dataset")
dim(dftrain)
print ("dimension of trimmed dataset")
dim(df)
library(randomForest)
#print ("Impute trimmed dataset if needed??")
#df.imputed <- rfImpute(classe ~ ., df)
```
We are using amazon aws 36 cpu node R-studio server;however,caret cannot installed
so we will do a random 90-10 random sample for validation against the benchmark

```{r}
trainNum=floor(dim(df)[1]*0.9)
trnIdx<-sample(nrow(df), trainNum)
df_trn=df[trnIdx, ]
df_tst=df[-trnIdx, ]
print ("dimension of train dataset")
dim(df_trn)
print ("dimension of test dataset")
dim(df_tst)
```
Now we use random forest with parallel like so
```{r}
library(doMC)
registerDoMC(cores=32)
library(foreach)
library(randomForest)
library(doParallel)
xx=df_trn[,-60]
yy=df_trn[,60]
rf <- foreach(ntree=rep(100, 32), .combine=combine, .multicombine=TRUE,
              .packages='randomForest') %dopar% {
                #randomForest(dat2[,-160], df$classe, ntree=ntree,nodesize=100,na.action=na.omit)
                #randomForest(classe~.,data=df, ntree=ntree,nodesize=100)
                #randomForest(x=xx,y=yy, ntree=ntree,nodesize=100,importance=TRUE)
                randomForest(classe~.,data=df_trn, ntree=ntree,nodesize=100)
              }


pred=predict(rf,df_tst[,-60])
#confusionMatrix(pred, df_tst$classe)
df_tst$pred<-pred
acc=dim(df_tst[df_tst$pred==df_tst$classe,])[1]/dim(df_tst)[1]
print("The overall accuracy without caret confusionMatrix")
format(round(acc, 4), nsmall = 4)
```

Predict the 20 cases 
```{r}
dftest<-read.table("/home/ubuntu/Downloads/pml-testing.csv", header=T, sep=",", na.strings=c("#DIV/0!","","NA"))
df_tst20 <- dftest[,colSums(is.na(dftrain))<nrow(dftrain)-1000]
df_tst20x<-df_tst20[,-60]
#df_tst20x$classe<-"X"
#str(df_trn)
#str(df_tst20x)
# $ magnet_dumbbell_z 
 #$ magnet_forearm_y
 #$ magnet_forearm_z
df_tst20x[,"magnet_dumbbell_z"] <- as.numeric(df_tst20x[,"magnet_dumbbell_z"])
df_tst20x[,"magnet_forearm_y"] <- as.numeric(df_tst20x[,"magnet_forearm_y"])
df_tst20x[,"magnet_forearm_z"] <- as.numeric(df_tst20x[,"magnet_forearm_z"])
#pred20=predict(rf,df_tst20x)

```
You can also embed plots, for example:

```{r, echo=FALSE}
#plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
